---
title: "baseball_salaries"
author: "Mark Duncan"
date: "11/4/2017"
output: html_document
---

Load the data for MLB players.

```{r}
library(ISLR)
names(Hitters)
dim(Hitters)
```

Check for missing data in Salary.

```{r}
sum(is.na(Hitters$Salary))
```

Remove the data rows that are missing salary data.

```{r}
Hitters = na.omit(Hitters)
dim(Hitters)
```

Perform a predictor selection by using the 'best subset selection' algorithm.  This procedure evaluates all model possibilities with a given number of predictors up to including all the predictors (e.g., for a set with 10 predictors, it evaluates all possible models with 0, 1, 2....10 predictors).  In the second step, the best model at each level of predictors are compared.

```{r}
library(leaps)
regfit.full = regsubsets(Salary ~ ., data = Hitters, nvmax=19)
reg.summary = summary(regfit.full)
reg.summary
```

Check the R^2 test statistic for each of the 19 top models.

```{r}
reg.summary$rsq
```

Plot the residual sum of squares, adjR2, Cp, and BIC for all 19 models.

```{r}

par(mfrow=c(2,2))
plot(reg.summary$rss, xlab="Number of Variables", ylab = "RSS")
plot(reg.summary$adjr2, xlab="Number of Variables", ylab="Adj RSq")
plot(reg.summary$cp, xlab="Number of Variables", ylab="Cp")
plot(reg.summary$bic, xlab="Number of Variables", ylab="BIC")
```

Find and highlight the max adjR2 and min for Cp and BIC.

```{r}
plot(reg.summary$adjr2, xlab="Number of Variables", ylab="Adj RSq")
adjr2_max = which.max(reg.summary$adjr2)
points(adjr2_max, reg.summary$adjr2[adjr2_max], col="red", cex=2, pch=20)

plot(reg.summary$cp, xlab="Number of Variables", ylab="Cp")
cp_min = which.min(reg.summary$cp)
points(cp_min, reg.summary$cp[cp_min], col="red", cex=2, pch=20)

plot(reg.summary$bic, xlab="Number of Variables", ylab="BIC")
bic_min = which.min(reg.summary$bic)
points(bic_min, reg.summary$bic[bic_min], col="red", cex=2, pch=20)
```

Examine the coefficients for the 6-predictor model:
```{r}
coef(regfit.full, 6)
```